\bibitem{RCapproch:paper}
Mantas Luko\v{s}evi\v{c}ius, Herbert Jaeger,
Reservoir computing approaches to recurrent neural network training,
Computer Science Review,
Volume 3, Issue 3,
2009,
Pages 127-149.
%ISSN 1574-0137,
%https://doi.org/10.1016/j.cosrev.2009.03.005.
%(http://www.sciencedirect.com/science/article/pii/S1574013709000173).

\bibitem{w} Wolfgang Maass, Thomas Natschläger, Henry Markram,
Real-time computing without stable states: A new frame-
work for neural computation based on perturbations, Neu-
ral Computation 14 (11) (2002) 2531–2560.

\bibitem{h} Herbert Jaeger, The “echo state” approach to analysing
and training recurrent neural networks, Technical Report
GMD Report 148, German National Research Center for
Information Technology, 2001.

\bibitem{Markovianfactor:paper}
Claudio Gallicchio, Alessio Micheli.
Architectural and Markovian factors of echo state networks,
Neural Networks,
Volume 24, Issue 5,
2011,
Pages 440-456.
%ISSN 0893-6080,
%https://doi.org/10.1016/j.neunet.2011.02.002.
%(http://www.sciencedirect.com/science/article/pii/S0893608011000530).

\bibitem{praticalguide}
Lukoševičius M. (2012) A Practical Guide to Applying Echo State Networks. In: Montavon G., Orr G.B., Müller KR. (eds) Neural Networks: Tricks of the Trade. Lecture Notes in Computer Science, vol 7700. Springer, Berlin, Heidelberg.

\bibitem{leakingintegrator}
Herbert Jaeger, Mantas Lukoševičius, Dan Popovici, Udo Siewert,
Optimization and applications of echo state networks with leaky- integrator neurons,
Neural Networks,
Volume 20, Issue 3,
2007,
Pages 335-352,
%ISSN 0893-6080,

%https://doi.org/10.1016/j.neunet.2007.04.016.

%(http://www.sciencedirect.com/science/article/pii/S089360800700041X)

